A prototype machine translation system for Kazakh and Tatar based on free/open-source components

### 2013-02-26 paper/paper.tex
remove/rename some of the Bashkir related stuff

\documentclass[11pt,a4paper]{article}
%\usepackage{lrec2012}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
\usepackage{times}
\usepackage{multirow}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

\title{A prototype machine translation system for Tatar and Bashkir based on 
   free/open-source components}

@@

\abstract{
This paper presents a prototype bidirectional machine translation system between 
Tatar and Bashkir, two minority Turkic languages of Russia. While the 
system has low open-domain coverage, results are presented that suggest
that high accuracy may be obtained between these two closely-related
languages, on a par with similar systems.
 \\
\Keywords{Tatar, Bashkir, MT, Free software, Open-source}
}

@@

This paper presents a prototype shallow-transfer rule-based machine translation
system between Tatar and Bashkir, two closely-related minority Turkic 
languages of Russia.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{mtsxiv}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
\usepackage{times}
\usepackage{multirow}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

\title{A prototype machine translation system for Kazakh and Tatar based on 
   free/open-source components}

@@

\abstract{
This paper presents a prototype bidirectional machine translation system between 
Kazakh and Tatar.
 \\
\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

@@

This paper presents a prototype shallow-transfer rule-based machine translation
system between Kazakh and Tatar.
